---
title: "Multivariate forecasting"
output: pdf_document #html_notebook
---

```{r setup, message=FALSE}
library(tidyverse)
source("multivariate_forecasting.R")
source("initialization_functions.R")
source("constrained_gls.R")
source("mle.R")
```

We will make a synthetic data set of 5 weeks of call volume from 2 streams, assuming each day is divided into 4 time intervals.

```{r}
set.seed(101)

df <- tibble(
  stream = rep(1:2, each = 5*7*4),
  call_volume = rpois(5*7*4*2, 5),
  wd = rep(1:7, 5*4*2),
  d = rep(1:(5*7), each = 4) %>% rep(2),
  t = rep(1:4, 5*7*2)
)
```

```{r}
head(df)
```

See the code in `multivariate_forecasting.R` for the function's documentation.

```{r, message=FALSE}
rslt <- multivariate_forecasting(
  df = df, 
  horizon = 7*4, # Forecast for one week into the future
  max_iter = 100, 
  algo = "NLOPT_LD_LBFGS",
  verbose = FALSE
)
```

```{r}
names(rslt)
```

The forecasts are given in a data frame, which can be accessed through the `df_pred` component of the resulting list.

```{r}
head(rslt$df_pred)
```

The estimated parameters of the model can be accessed through the `params` component of the resulting list.

```{r}
rslt$params
```




